---
title: "Cp3_assignment_1_instructions"
author: "Aidan O'Hara"
date: "2023-08-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Factorial, Fibonacci, and Foobar examples

# Exercise 1

Re-create the factorial function, `factorial()` without calling the factorial function. Think about what inputs are appropriate for your function, and have your function return an `"Error"` string if provided an invalid input. Call your function `myFactorial`.

```{r}
# Examples #

> myFactorial(5)
[1] 120

> myFactorial(-2)
[1] "Error"
```




# Exercise 2

Write a function that returns a vector of the first n elements of the Fibonacci sequence, starting with 0,1,...
Call your function `myFib`

```{r}
# Examples #

> myFib(12)
[1]  0  1  1  2  3  5  8 13 21 34 55 89

> myFib(-2)
NULL

```


# Exercise 3

Write a function called `fooBarFun` that takes a number for an input, if the number is divisible by 3 the function should return the string "Foo", if the number is divisible by 5 the function should return the string "Bar".  Finally if the number is divisible by both 3 and 5 the function should return the string "FooBar".  Return an empty string if the number is not divisible by 3 or 5.  Use `%%` to check for divisibility and `paste0` to construct your string returns.

```{r}
# Examples #

> fooBarFun(3)
[1] "Foo"

> fooBarFun(5)
[1] "Bar"

> fooBarFun(15)
[1] "FooBar"
```